Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance

### 2022-11-17 Manuscript/UpdatedBlockBootstrap.Rmd

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sqrt((sd^2)*(1-theta^2)))

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  value = 0
  if (identical(statistic, ar1))
  {
    value = theta
  }
  if (nm_interval[1] < value && nm_interval[2] > value)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < value && mv_interval[2] > value)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}

do1rep2 <- function(n, theta, sd, l, statistic) {
  x <- rnorm(n = n, sd = sd)

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  value = 0
  if (identical(statistic, ar1))
  {
    value = theta
  }

  if (nm_interval[1] < value && nm_interval[2] > value)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < value && mv_interval[2] > value)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}
```

@@

```{r}
#m_norm_1024 <- c(1024, m_norm_1024)
```

```{r}
m_norm <- data.frame(rbind(t(m_norm_32[c(1, 6, 17, 16)]), t(m_norm_32[c(1, 10, 19, 18)]), t(m_norm_64[c(1, 6, 17, 16)]), t(m_norm_64[c(1, 10, 19, 18)]), t(m_norm_128[c(1, 6, 17, 16)]), t(m_norm_128[c(1, 10, 19, 18)]), t(m_norm_256[c(1, 6, 17, 16)]), t(m_norm_256[c(1, 10, 19, 18)]), t(m_norm_512[c(1, 6, 17, 16)]), t(m_norm_512[c(1, 10, 19, 18)]), t(m_norm_1024[c(1, 6, 17, 16)]), t(m_norm_1024[c(1, 10, 19, 18)])))
rownames(m_norm) <- NULL
colnames(m_norm) <- c("n", 'coverage_rate', 'lb', 'ub')
m_norm['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
m_norm[order(-m_norm$n), ]
```

>>>>

do1rep <- function(n, theta, sigma,
                   target,
                   len, statistic, B = 1000) {
  x <- arima.sim(list(ar = theta), n = n, sd = sigma * sqrt(1-theta^2))
  ## sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
  bt <- blkboot(x, statistic, B, len)

  ## two intervals  
  nm = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm.cov <- nm[1] < target && target < nm[2]
  mv.cov <- mv[1] < target && target < mv[2]

  ## c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

  ## returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
  c(nm.cov, mv.cov)
}

@@

```{r}
#m_norm_1024 <- c(1024, m_norm_1024)
# Save the simulation results to an external file
```

```{r}
## put the processing of the results in a separate script
## load the simulation results
m_norm <- data.frame(rbind(t(m_norm_32[c(1, 6, 17, 16)]), t(m_norm_32[c(1, 10, 19, 18)]), t(m_norm_64[c(1, 6, 17, 16)]), t(m_norm_64[c(1, 10, 19, 18)]), t(m_norm_128[c(1, 6, 17, 16)]), t(m_norm_128[c(1, 10, 19, 18)]), t(m_norm_256[c(1, 6, 17, 16)]), t(m_norm_256[c(1, 10, 19, 18)]), t(m_norm_512[c(1, 6, 17, 16)]), t(m_norm_512[c(1, 10, 19, 18)]), t(m_norm_1024[c(1, 6, 17, 16)]), t(m_norm_1024[c(1, 10, 19, 18)])))
rownames(m_norm) <- NULL
colnames(m_norm) <- c("n", 'coverage_rate', 'lb', 'ub')
m_norm['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
m_norm[order(-m_norm$n), ]
```
